On Designing Collusion-Resistant Incentive Mechanisms for Mobile Crowdsensing Systems

### 2015-11-28 techreport.tex
Committer: Shiyu Ji <shiyu@csil.cs.ucsb.edu>
On branch master
Your branch is up-to-date with 'origin/master'.

Changes to be committed:
new file:   13fall_1ed.bib
new file:   collusion_resist_codes/Makefile
new file:   collusion_resist_codes/images/img_gs_perturb_con.eps
new file:   collusion_resist_codes/images/img_gs_perturb_dis.eps
new file:   collusion_resist_codes/images/img_gs_ratio_con.eps
new file:   collusion_resist_codes/images/img_gs_ratio_dis.eps
new file:   collusion_resist_codes/images/img_pk.eps
new file:   collusion_resist_codes/images/img_tk.eps
new file:   collusion_resist_co

\renewcommand{\baselinestretch}{0.985}
%\setlength{\textfloatsep}{10pt}
%\setlength{\abovecaptionskip}{10pt}

@@

With the tremendous popularity of smartphones and other portable devices, crowdsensing applications have become a center of attention in recent years. Different mechanisms (e.g., auctions) have been designed to incentivize mobile users to participate in crowdsensing. However, there are still many open issues needed to be investigated for these incentive mechanisms. 
In this paper, for the first time, we systematically study the collusion resistance issue for incentive mechanisms in crowdsensing applications. %To the best of our knowledge, we are the first to investigate the collusion resistant incentive mechanisms for crowdsensing applications. 
For a typical type of crowdsensing scenarios, we find two fundamental criteria: One is to judge whether a truthful incentive mechanism can resist any collusion without profit trading by achieving group strategyproof equilibrium, and the other is to judge whether a truthful mechanism can defend against any collusion even with profit trading by achieving t-truthful equilibrium. These criteria can be straightforwardly applied and have direct practical benefits. Furthermore, we also propose our solution that can resist any form of collusion attacks, even including profit trading among the attackers. We conduct extensive experiments to verify our theoretical results and evaluate the security performance of our proposed mechanisms. 
\end{abstract}
}

\section{Introduction}
With the rapidly increasing use of portable devices (e.g., smartphones), there are plenty of research works \cite{ganti2011mobile, vukovic2010ubiquitous, cortes2002coverage} and numerous applications \cite{nawaz2013parksense, rai2012zee, yan2011crowdpark, kazman2009metropolis} on mobile sensing. Sensing apps on smartphones allow people to sense and collect different kinds of information ubiquitously. 
To sufficiently explore the sensing capability of each sensor within the network, crowdsensing \cite{ganti2011mobile} \cite{howe2006rise} techniques can be applied. For instance, by using the  crowdsensing platform, we can access the up-to-date parking slots information on the neighboring community \cite{nawaz2013parksense, yan2011crowdpark}, or monitor weather changes \cite{kazman2009metropolis}.

The incentive issues in crowdsensing systems have been extensively studied \cite{yang2012crowdsourcing, zhang2012reputation, koutsopoulos2013optimal, singla2013truthful, jaimes2012location}. Crowdsensing work embodies costs in nature (e.g., service fees, battery usage, etc). Hence, we need to stimulate the participating users to contribute their sensed data,  by giving them incentives (e.g., in monetary forms) to cover the cost incurred by individual sensing activities. Existing incentive mechanisms (e.g., \cite{yang2012crowdsourcing, zhang2012reputation, jaimes2012location}) use game theoretical approaches to achieve different equilibria. For instance, strategyproof crowdsensing incentive mechanisms \cite{moulin2001strategyproof, chen2013sparc, feng2013imac} can guarantee that it is to the best interest of each participating user to honestly report their information such as sensing cost. However, strategyproofness cannot eliminate the possibility that a group of users collaborate to cheat in the system and harm the system or other users' utility. 
Unfortunately, there has not been any existing work that systematically investigates the collusion attack problem in crowdsensing incentive mechanisms.
%These mechanisms usually need to know some information about each user (i.e. sensing cost and revenue). However, for many cases we cannot guarantee the participatory users are always honest. In other words, some users may give false reports deceitfully. Hence strategyproofness (or truthfulness) arises to eliminate these cheatings . Strategyproof incentive mechanism is safe to use for any participatory user, assuming the users are \emph{selfish} and never trust each other completely. This implies strategyproofness is not strong enough to defend against collusion attack, in which group of users have complete trust between each other.

@@

In real-world crowdsensing applications, a single entity may simultaneously own a number of mobile devices, e.g., smartphones, laptops, tablets, watches, etc. These devices may have diverse sensing costs and can participate the same crowdsensing task. In the crowdsensing procedure, since the payment that each user receives is usually correlated to its sensing contribution and the involved cost, the same owner can manipulate a group of devices' sensing strategies at the same time and make them collaboratively cheat (e.g., reporting carefully-calculated fake cost information to rule out other potential participants) for better payoffs as a collusion. It creates serious problems for the platform, such as losing system-wide utility and deteriorating other users' enthusiasm to participate.
%Many existing crowdsensing incentive mechanisms \cite{yang2012crowdsourcing,koutsopoulos2013optimal,zheng2014strategy} that assume individual rationality cannot .

Collusion attack is an important but difficult problem to address in general \cite{zhong2007designing, wang2006low, jurca2007collusion}. 
The difficulty lies in two aspects: \textbf{1)} A variety of collusion strategies (e.g., with or without profit trading) make the design of counter-measure challenging. It means that in practice it requires security expertise to consider as many collusion scenarios as possible for a specific setting and provide technical solutions to mitigate the known collusion attacks. But like other penetration analysis, there is no guarantee of guard against unexamined cases. \textbf{2)} Difficulty exists when trying to provide theoretical guarantee of guard in the incentive mechanism design. 
As we mentioned earlier, since strategyproofness cannot provide collusion resistance \cite{zhong2007designing}, people try to use other game theoretical solution concepts, such as \emph{Group Strategyproof Equilibrium} \cite{jain1999group} to achieve collusion resistance. %So far  is one of the standard collusion resistant solutions that can give truthful mechanisms.
However, within the scope of wireless networks, sometimes it is not possible at all to achieve any group strategyproof equilibrium in some games. For example, one can never achieve any group strategyproofness in theory for noncooperative routing games in wireless ad hoc networks \cite{zhong2007designing}. When the possibility that colluding nodes can trade profit among them, this problem becomes even harder. For the same routing problem, we cannot obtain any strategyproofness if the colluding users can trade profit among them \cite{wang2006low}.

@@

In this paper we systematically study the collusion-resistance problem in crowdsensing incentive mechanism design. Our goals are not only to provide theoretical results, for example, on the possibility of achieving group strategyproofness, but also to make the theoretical results have direct benefits in practice. In particular, we notice that even with the formal definition of group-strategyproofness and \textit{t-truthfulness} (defense against profit trading), it is very challenging for mobile crowdsensing practitioners to map the theoretical definitions to their concrete systems that they have or are about to design. In this paper, we will provide much more straightforward criteria/techniques to judge whether a given incentive mechanism is group-strategyproof or t-truthful, so that the designer or practitioners can easily apply. This effort has significant benefits in reducing unnecessary overhead and meanwhile maintains the security guarantee. For instance, if we can easily determine that the incentive mechanism can intrinsically defend against profit trading by achieving t-truthfulness, then we do not have to use extra cryptographic protocols, such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing}. Thus the computation and communication overhead are reduced.

@@

\bolditem We investigate a popular type of crowdsensing games, in which each contributing user takes some sensing time to finish the assigned tasks and to earn the promised payment from the platform. We not only find that it is feasible to design group strategyproof incentive mechanisms for this type of crowdsensing game, but also obtain the straightforward criteria to judge whether a given strategy-proof incentive mechanism can achieve group strategyproofness. Moreover, we rigorously derive the criteria to judge whether a truthful mechanism is t-truthful to guard against profit trading. %In other words, we show that it is theoretically possible to resist any collusion attack, even with profit trading, for the crowdsensing game. 
%By correctly judging whether an incentive mechanism can resist collusion or profit trading, we can gain many benefits in the real world. For example, \cite{archer2004approximation} has given the truthful incentive mechanism that can successfully defend against collusion in multicast cost sharing by achieving group strategyproofness. If each user cannot trust others completely, the information from the users can be reliable and the system does not have to use extra protocols to ensure no one is cheating. In this light, we can obtain reliable information and save communication overhead if we can show the truthful incentive mechanism can achieve group strategyproofness. %For the scenario of wireless ad hoc routing, \cite{zhong2007designing} has given the collusion resistant incentive mechanism that cannot achieve n-truthfulness. That is, their proposed incentive mechanism cannot solely eliminate the possibility of profit trading. This implies that one has to take additional actions to rigorously defend against profit trading, for example, by leveraging some public cryptographic protocols such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing}. In other words, if we can show the incentive mechanism can intrinsically defend against profit trading by achieving n-truthfulness, then we do not have to use the extra cryptographic protocols and hence reduce the computation and communication overhead. Hence our obtained criteria can give practical benefits.} %Furthermore, based on both the obtained criteria, we propose a concrete incentive mechanism which is not only collusion resistant, but also maximizes the platform utility.

@@

\bolditem To verify our theoretic results, we also perform extensive simulations, and show that all the experimental results support our findings.

@@

\subsection{Crowdsensing Game}
\label{subsec:CG}
{
We introduce the general game model of crowdsensing system, which is used in the majority of existing literatures \cite{yang2012crowdsourcing,koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social,yan2015ifc}. The crowdsensing system consists of $n$ participating users, who are \emph{willing} to contribute in the crowdsensing work, e.g., smartphones, mobile sensors, and one crowdsensing platform (e.g., BOINC \cite{anderson2004boinc}). The $n$ users voluntarily participate in crowdsensing and contribute their sensing results. The platform aggregates the sensing results from the $n$ users and maintains the crowdsensing system. %For each contributing user\footnote{contributing users are the users who \emph{actually} participate in the crowdsensing by \emph{contributing} sensing work.}, sensing work incurs cost in monetary form, such as battery charge and communication fees. 
To compensate the users' sensing costs and stimulate their participation, the platform distributes some payment to each user as the reward. The payment is determined by each user's strategy (i.e., its claimed sensing cost). Denote by $c_i$ the sensing cost of user $i$, and let $p_i$ be the promised payment from the platform to user $i$. If user $i$ can complete the sensing task as promised, then the utility of user $i$ is
\begin{equation}
\label{eqn:user_utility_1}
u_i = p_i-c_i.
\end{equation}
%Here the utility is the incentive for each user to participate in crowdsensing. 
Due to individual rationality, each user wants to maximize its own utility. %To address the incentive issues, we need an incentive mechanism, which is an interactive scheme between the users and the platform to determine the payment to each user.

We next analyze the platform utility. {Based on the ideas of \cite{yang2012crowdsourcing,luo2014profit,zhang2014free,liu2014social}}, the platform utility has a diminishing return on the contribution of each user. \cite{yan2015ifc} gives the idea to calculate the contributed gain from all the contributing users by summation over $U$. That is, we have its closed-form as following:
\begin{equation}
\label{eqn:plat_utility}
u_p=\sum_{i\in U}\lambda_i\log (1+t_i)-p_i.
\end{equation}
%Here $R$ is the baseline reward (i.e. the fixed reward as the crowdsensing finishes certain tasks).\footnote{In many existing models such as \cite{yang2012crowdsourcing}, there is no fixed baseline reward, and the gain primarily relies on the collected information. If so, $R=0$. If there are some external fundings provided by people who will use the collected information, then $R>0$.} {\color{black}As in Section \ref{sec:opu}, a positive baseline reward can well guarantee the participation of the platform, i.e. $R>0$.} $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing works, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working since it is making money.
Here $\lambda_i$ is a fixed parameter for each user $i$. By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing literatures, such as \cite{yang2012crowdsourcing,zhang2014free}. $t_i$ is the measurement of user $i$\rq{}s contribution (e.g., sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working.
}

@@

%\subsection{Differential Privacy}
%Our discussions on privacy preservation of the discrete crowdsensing model will use the conception of differential privacy \cite{dwork2006differential}. We give its formal definition here. Differential privacy scheme takes the threat model as a randomized algorithm that tries to find the real identities of interesting users, and scrutinizes whether there exists a significantly distinguished successful probability.
%\begin{definition}
%\label{def:dp}
%\textbf{(Differential Privacy)} A randomized algorithm $\mathbf{A}$ takes the dataset from an anonymous user and returns the identity of the user. Denote by $i$ the identity of user $i$. Let $n_i$ denote the dataset from user $i$. Then the randomized algorithm $\mathbf{A}$ is $\varepsilon$-differentially private if for any users $i$, $j$, for any subset $S \subseteq U$, we have
%\begin{equation}
%\label{eqn:dp}
%\operatorname{Pr}(\mathbf{A}(n_i) \in S) \leq e^{\varepsilon}\operatorname{Pr}(\mathbf{A}(n_j) \in S).\footnote{Here each element in $S$ is a user identity, like $i$, $j$.}
%\end{equation}
%\end{definition}
%For our crowdsensing system, if every allowed\footnote{We assume our system can disallow any illegal transactions, i.e. hacking into the user to obtain its real identity, or cheating by emails, by using cryptographic techniques and administrative procedures. Hence we may only consider the allowed operations, e.g., traffic analysis, timing attack, etc.} randomized algorithm is $\varepsilon$-differentially private, we say our system preserves $\varepsilon$-differential privacy.

@@

\subsection{\color{black} A Typical Strategyproof Crowdsensing Game}
We have discussed the basics of crowdsensing games in Section \ref{subsec:CG}. However, we have not given any closed-form of each user\rq{}s sensing cost $c_i$. According to \cite{koutsopoulos2013optimal}, the sensing cost should increase with the user\rq{}s participation level. For real-world applications, usually sensing time can be a good metric of each user's participation. For example, more time the user spends on sensing, more sensed data the user can contribute, and more sensing cost may be incurred. We denote by $t_i$ the sensing time (or participation level in more general sense) of user $i$, and let $\kappa_i$ be the cost unit of user $i$. Then we have the cost $c_i=\kappa_it_i$. Given (\ref{eqn:user_utility_1}), we have
\begin{equation}
\label{eqn:user_utility_2}
u_i = p_i-\kappa_it_i.
\end{equation}
Here the cost unit $\kappa_i$ is \emph{private information} owned only by user $i$, since $\kappa_i$ is closely associated with individual attributes (e.g., battery capacity, smartphone types, etc.). Since each user $i$ has no knowledge of others\rq{} real-time cost units $\kappa_{-i}$, it is impossible to directly leverage the platform-centric incentive mechanism in \cite{yang2012crowdsourcing}. However, we can let each user declare its own cost unit as a strategy (like \cite{zhong2007designing} did). If we can propose an incentive mechanism that can achieve strategyproof equilibrium, the platform can know the cost units globally based on each user\rq{}s truthful strategy.

We now present a general incentive mechanism that can achieve strategyproof equilibrium. Since the platform has no preknowledge about any user\rq{}s cost unit, the users need to upload \emph{claimed} cost units to the platform, and then the platform determines the payment and required sensing time of each user. The detailed procedures are as follows:
\begin{enumerate}
\item Each user $i$ uploads its claimed cost unit $s_i$ (can be different from $\kappa_i$) to the platform;
\item The platform calculates the payment $p_i$ and required sensing time $t_i$ of each user $i$ based on all the claimed cost units $s_1,s_2,\cdots,s_n$;
\item The platform lets each user $i$ know its payment $p_i$ and required sensing time $t_i$;
\item Each user must finish its required sensing time to earn the payment. Each user can also quit the crowdsensing to avoid deficit;
\item The users, who have finished the sensing time, upload the sensed data to the platform;
\item The platform verifies the uploaded data and confirms the payment.
\end{enumerate}
To be strategyproof, our incentive mechanism requires all users to be honest on their claimed cost units $s_i$. That is, we desire $s_i = \kappa_i$ for each user $i$. To achieve this goal, we need delicate closed-forms of payment $p_i$ and required sensing time $t_i$. It turns out that the concrete mechanism design is open-ended and there exist many different solutions. Since there are extensive literatures \cite{koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social} on the solutions to achieve strategyproofness in similar scenarios, we leave the discussions in Appendix of our technical report \cite{techrpt}.

\subsection{An Example of Collusions in Strategyproof crowdsensing Game}
Unfortunately, a strategyproof incentive mechanism is usually not strong enough to resist collusions rigorously. 
{\color{black}
For example, suppose a game has two users $i,j$ s.t. $\kappa_i = \kappa_j = 1$. Given the user strategies $s_i$ and $s_j$ (claimed cost), for user $i$ suppose the platform assigns its sensing time as $t_i(s_i, s_j)=s_j\mathrm{e}^{-s_i}$ and the incentive mechanism lets its payment be $p_i(s_i, s_j)
%=s_it_i(s_i, s_j)+\int_{s_i}^{+\infty}t_i(s, s_j)\mathrm{d}s
=(s_i+1)s_j\mathrm{e}^{-s_i}.$ The case of user $j$ is analogous. Thus the user utilities are 
\begin{equation}
\begin{aligned}
u_i(s_i,s_j)=&p_i(s_i, s_j)-\kappa_it_i(s_i, s_j) \\
=&(s_i+1)s_j\mathrm{e}^{-s_i} - 1\times s_j\mathrm{e}^{-s_i} \\
=&s_js_i\mathrm{e}^{-s_i},\\
\end{aligned}
\end{equation}
and similarly $u_j(s_i,s_j)=s_is_j\mathrm{e}^{-s_j}$. 
}

>>>>

\renewcommand{\baselinestretch}{0.98}
\setlength{\textfloatsep}{10pt}
\setlength{\abovecaptionskip}{10pt}

@@

With the rise of smartphones, crowdsensing applications have tremendously increasing trending. As a result, many incentive issues are worth researching. In this paper, we give detailed discussions on collusion resistant incentive mechanisms for crowdsensing applications. Two fundamental criteria are found: one is to judge whether a truthful incentive mechanism can resist any collusion without profit trading by achieving group strategyproof equilibrium, and the other is to judge whether a truthful mechanism can defend against any collusion even with 
profit trading by achieving t-truthful equilibrium. Furthermore, we also propose our solution which can resist any form of collusion attack, even including profit trading among the attackers. Extensive simulations verify our results. To the best of our knowledge, we are the first to investigate the collusion resistant incentive mechanisms for crowdsensing applications.
\end{abstract}
}

\section{Introduction}
With the rapidly increasing use of portable devices (e.g. smartphones), there are plenty of research works \cite{ganti2011mobile, vukovic2010ubiquitous, cortes2002coverage} and numerous applications \cite{nawaz2013parksense, rai2012zee, yan2011crowdpark, kazman2009metropolis} on mobile sensing. Sensing apps on smartphones allow people to sense and collect different kinds of information ubiquitously. 
To sufficiently explore the sensing capability of each sensor within the network, crowdsensing \cite{howe2006rise} \cite{ganti2011mobile} techniques can be applied. For instance, by using the  crowdsensing platform, we can access the up-to-date parking slots information on the neighboring community \cite{nawaz2013parksense, yan2011crowdpark}, or monitor weather changes \cite{kazman2009metropolis}.

The incentive issues in crowdsensing systems have been extensively studied \cite{yang2012crowdsourcing, zhang2012reputation, koutsopoulos2013optimal, singla2013truthful, jaimes2012location}. Crowdsensing work embodies costs in nature (e.g. service fees, battery usage, etc). Hence we need to stimulate the participating users to contribute their sensed data,  by giving them some incentives (e.g., in monetary forms) to cover the cost incurred by individual sensing activities. Existing incentive mechanisms (e.g., \cite{yang2012crowdsourcing, zhang2012reputation, jaimes2012location}) use game theoretical approaches to achieve different equilibria. For instance, strategyproof crowdsensing incentive mechanisms\cite{moulin2001strategyproof, chen2013sparc, feng2013imac} can guarantee that it is to the best interest of each participating user to honestly report their information such as sensing cost. However, strategyproofness cannot eliminate the possibility that a group of users collaborate to cheat in the system and harm the system or other users' utility. 
Unfortunately, there has not been any existing work that systematically investigates the collusion attack problem in crowdsensing incentive mechanisms.
%These mechanisms usually need to know some information about each user (i.e. sensing cost and revenue). However, for many cases we cannot guarantee the participatory users are always honest. In other words, some users may give false reports deceitfully. Hence strategyproofness (or truthfulness) arises to eliminate these cheatings . Strategyproof incentive mechanism is safe to use for any participatory user, assuming the users are \emph{selfish} and never trust each other completely. This implies strategyproofness is not strong enough to defend against collusion attack, in which group of users have complete trust between each other.

@@

In real-world crowdsensing applications, a single entity may simultaneously own a number of mobile devices, e.g. smartphones, laptops, tablets, watches, etc. These devices may have diverse sensing costs and but can participate the same crowdsensing task. In the crowdsensing procedure, since the payment that each user receives is usually correlated to its sensing contribution and the involved cost, the same owner can manipulate a group of devices' sensing strategies at the same time and make them collaboratively cheat (e.g., reporting carefully-calculated fake cost information to rule out other potential participants) for better payoffs as a collusion. It creates serious problems for the platform, such as losing system-wide utility and deteriorating other users' enthusiasm to participate.
%Many existing crowdsensing incentive mechanisms \cite{yang2012crowdsourcing,koutsopoulos2013optimal,zheng2014strategy} that assume individual rationality cannot .

Collusion attack is an important but difficult problem to address in general \cite{zhong2007designing, wang2006low, jurca2007collusion}. 
The difficulty lies in two aspects: \textbf{1)} A variety of collusion strategies (e.g., with or without profit trading) make the mitigation challenging. It means that in practice it requires security expertise to consider as many collusion scenarios as possible for a specific setting and provide technical solutions to mitigate the known collusion attacks. But like other penetration analysis, there is no guarantee of guard against unexamined cases. \textbf{2)} Difficulty exists when trying to provide theoretical guarantee of guard in the incentive mechanism design. 
As we mentioned earlier, since only strategyproofness cannot provide collusion resistance \cite{zhong2007designing}, people try to use other game theoretical solution concepts such as \emph{Group Strategyproof Equilibrium} \cite{jain1999group} to achieve collusion resistance. %So far  is one of the standard collusion resistant solutions that can give truthful mechanisms.
However, within the scope of wireless networks, sometimes it is not possible at all to achieve any group strategyproof equilibrium in some games. For example, one can never achieve any group strategyproofness in theory for noncooperative routing games in wireless ad hoc networks \cite{zhong2007designing}. When the possibility that colluding nodes can trade profit among them, this problem becomes even harder. For the same routing problem, we cannot obtain any strategyproofness if the colluding users can trade profit among them \cite{wang2006low}.

@@

In this paper we systematically study the collusion-resistance problem in crowdsensing incentive mechanism design. Our goals are not only to provide theoretical results, for example, on the possibility of achieving group strategyproofness, but also to make the theoretical results have direct benefits in practice. In particular, we notice that even with the formal definition of group-strategyproofness and \textit{t-truthfulness} (defense against profit trading), it is very challenging for mobile crowdsensing practitioners to map the theoretical definitions to their concrete systems that they have or are about to design. In this paper, we will provide much more straightforward criteria/techniques to judge whether a given incentive mechanism is group-strategyproof or t-truthful, so that the designer or practitioners can easily apply. This effort has significant benefits in reducing unnecessary overhead and meanwhile maintains the security guarantee. For instance, if we can easily determine that the incentive mechanism can intrinsically defend against profit trading by achieving t-truthfulness, then we do not have to use extra cryptographic protocols such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing} that are used to restrict profit trading. Thus the computation and communication overhead are reduced.

@@

\bolditem We investigate a popular type of crowdsensing games, in which each contributing user takes some sensing time to finish the assigned tasks and earns the promised payment from the platform. We not only find it is feasible to design group strategyproof incentive mechanisms for this type of crowdsensing game, but also obtain the straightforward criteria to judge whether a given strategy-proof incentive mechanism can achieve group strategyproofness. Moreover, we rigorously derive the criteria to judge whether a truthful mechanism is t-truthful to guard against profit trading. %In other words, we show that it is theoretically possible to resist any collusion attack, even with profit trading, for the crowdsensing game. 
%By correctly judging whether an incentive mechanism can resist collusion or profit trading, we can gain many benefits in the real world. For example, \cite{archer2004approximation} has given the truthful incentive mechanism that can successfully defend against collusion in multicast cost sharing by achieving group strategyproofness. If each user cannot trust others completely, the information from the users can be reliable and the system does not have to use extra protocols to ensure no one is cheating. In this light, we can obtain reliable information and save communication overhead if we can show the truthful incentive mechanism can achieve group strategyproofness. %For the scenario of wireless ad hoc routing, \cite{zhong2007designing} has given the collusion resistant incentive mechanism that cannot achieve n-truthfulness. That is, their proposed incentive mechanism cannot solely eliminate the possibility of profit trading. This implies that one has to take additional actions to rigorously defend against profit trading, for example, by leveraging some public cryptographic protocols such as Designated Verifier Signatures \cite{jakobsson1996designated} or Restricted Verifier Signatures \cite{zhong2007designing}. In other words, if we can show the incentive mechanism can intrinsically defend against profit trading by achieving n-truthfulness, then we do not have to use the extra cryptographic protocols and hence reduce the computation and communication overhead. Hence our obtained criteria can give practical benefits.} %Furthermore, based on both the obtained criteria, we propose a concrete incentive mechanism which is not only collusion resistant, but also maximizes the platform utility.

@@

\bolditem To verify our theoretic results, we also perform extensive simulations, and we show that all the experimental results support our findings.

@@

\subsection{Crowdsensing Game}
\label{subsec:CG}
{
We introduce the general game model of crowdsensing system, which is used in the majority of existing literatures \cite{yang2012crowdsourcing,koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social,yan2015ifc}. The crowdsensing system consists of $n$ participating users\footnote{Participating users are all the users who are \emph{willing} to contribute in the crowdsensing work.} (i.e. smartphones, mobile sensors) and one crowdsensing platform (i.e. BOINC \cite{anderson2004boinc}). The $n$ users voluntarily participate in crowdsensing and contribute their sensing results. The platform aggregates the sensing results from the $n$ users and maintains the crowdsensing system. %For each contributing user\footnote{contributing users are the users who \emph{actually} participate in the crowdsensing by \emph{contributing} sensing work.}, sensing work incurs cost in monetary form, such as battery charge and communication fees. 
To compensate the users' sensing costs and stimulate their participation, the platform distributes some payment to each user as the reward. The payment is determined by each user's strategy (i.e., its claimed sensing cost). Denote by $c_i$ the sensing cost of user $i$, and let $p_i$ be the promised payment from the platform to user $i$. If user $i$ can complete the sensing task as promised, then the utility of user $i$ is
\begin{equation}
\label{eqn:user_utility_1}
u_i = p_i-c_i.
\end{equation}
%Here the utility is the incentive for each user to participate in crowdsensing. 
Due to individual rationality, each user wants to maximize its own utility. %To address the incentive issues, we need an incentive mechanism, which is an interactive scheme between the users and the platform to determine the payment to each user.

We next analyze the platform utility. {Based on the ideas of \cite{yang2012crowdsourcing,luo2014profit,zhang2014free,liu2014social}}, the platform utility has a diminishing return on the contribution of each user. \cite{yan2015ifc} gives the idea to calculate the contributed gain from all the contributing users by summation over $U$. That is, we have its closed-form as following:
\begin{equation}
\label{eqn:plat_utility}
u_p=\sum_{i\in U}\lambda_i\log (1+t_i)-p_i.
\end{equation}
%Here $R$ is the baseline reward (i.e. the fixed reward as the crowdsensing finishes certain tasks).\footnote{In many existing models such as \cite{yang2012crowdsourcing}, there is no fixed baseline reward, and the gain primarily relies on the collected information. If so, $R=0$. If there are some external fundings provided by people who will use the collected information, then $R>0$.} {\color{black}As in Section \ref{sec:opu}, a positive baseline reward can well guarantee the participation of the platform, i.e. $R>0$.} $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing works, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working since it is making money.
Here $\lambda_i$ is a fixed parameter for each user $i$,\footnote{By assigning different $\lambda_i$, we can handle the scenarios that the platform treats the users with different weights. This generalizes the uniform weight assumption in some existing literatures, such as \cite{yang2012crowdsourcing,zhang2014free}.} and $t_i$ is the measurement of user $i$\rq{}s contribution (i.e. sensing time or sensed data). We must guarantee the platform utility $u_p>0$ so that our crowdsensing can keep working.
}

@@

%\subsection{Differential Privacy}
%Our discussions on privacy preservation of the discrete crowdsensing model will use the conception of differential privacy \cite{dwork2006differential}. We give its formal definition here. Differential privacy scheme takes the threat model as a randomized algorithm that tries to find the real identities of interesting users, and scrutinizes whether there exists a significantly distinguished successful probability.
%\begin{definition}
%\label{def:dp}
%\textbf{(Differential Privacy)} A randomized algorithm $\mathbf{A}$ takes the dataset from an anonymous user and returns the identity of the user. Denote by $i$ the identity of user $i$. Let $n_i$ denote the dataset from user $i$. Then the randomized algorithm $\mathbf{A}$ is $\varepsilon$-differentially private if for any users $i$, $j$, for any subset $S \subseteq U$, we have
%\begin{equation}
%\label{eqn:dp}
%\operatorname{Pr}(\mathbf{A}(n_i) \in S) \leq e^{\varepsilon}\operatorname{Pr}(\mathbf{A}(n_j) \in S).\footnote{Here each element in $S$ is a user identity, like $i$, $j$.}
%\end{equation}
%\end{definition}
%For our crowdsensing system, if every allowed\footnote{We assume our system can disallow any illegal transactions, i.e. hacking into the user to obtain its real identity, or cheating by emails, by using cryptographic techniques and administrative procedures. Hence we may only consider the allowed operations, i.e. traffic analysis, timing attack, etc.} randomized algorithm is $\varepsilon$-differentially private, we say our system preserves $\varepsilon$-differential privacy.

@@

\subsection{\color{black} A Typical Strategyproof Crowdsensing Game}
We have discussed the basics of crowdsensing games in Section \ref{subsec:CG}. However, we have not given any closed-form of each user\rq{}s sensing cost $c_i$. According to \cite{koutsopoulos2013optimal}, the sensing cost should increase with the user\rq{}s participation level. For real-world applications, usually sensing time can be a good metric of each user's participation. For example, more time the user spends on sensing, more sensed data the user can contribute, and more sensing cost may be incurred. We denote by $t_i$ the sensing time (or participation level in more general sense) of user $i$, and let $\kappa_i$ be the cost unit of user $i$. Then we have the cost $c_i=\kappa_it_i$. Given (\ref{eqn:user_utility_1}), we have
\begin{equation}
\label{eqn:user_utility_2}
u_i = p_i-\kappa_it_i.
\end{equation}
Here the cost unit $\kappa_i$ is \emph{private information} owned only by user $i$, since $\kappa_i$ is closely associated with individual attributes (i.e., battery capacity, smartphone types, etc.). Since each user $i$ has no knowledge of others\rq{} real-time cost units $\kappa_{-i}$, it is impossible to directly leverage the platform-centric incentive mechanism in \cite{yang2012crowdsourcing}. However, we can let each user declare its own cost unit as a strategy (like \cite{zhong2007designing} did). If we can propose an incentive mechanism that can achieve strategyproof equilibrium, the platform can know the cost units globally based on each user\rq{}s truthful strategy.

We now present a general incentive mechanism that can achieve strategyproof equilibrium. Since the platform has no preknowledge about any user\rq{}s cost unit, the users need to upload \emph{claimed} cost units to the platform, and then the platform determines the payment and required sensing time of each user. The detailed procedures are as follows:
\begin{enumerate}
\item Each user $i$ uploads its claimed cost unit $s_i$ (can be different from $\kappa_i$) to the platform;
\item The platform calculates the payment $p_i$ and required sensing time $t_i$ of each user $i$ based on all the claimed cost units $s_1,s_2,\cdots,s_n$;
\item The platform lets each user $i$ know its payment $p_i$ and required sensing time $t_i$;
\item Each user must finish its required sensing time to earn the payment. Each user can also quit the crowdsensing to avoid deficit;
\item The users, who have finished the sensing time, upload the sensed data to the platform;
\item The platform verifies the uploaded data and confirms the payment.
\end{enumerate}
To be strategyproof, our incentive mechanism requires all users to be honest on their claimed cost units $s_i$. That is, we desire $s_i = \kappa_i$ for each user $i$. To achieve this goal, we need delicate closed-forms of payment $p_i$ and required sensing time $t_i$. It turns out that the concrete mechanism design is open-ended and there exist many different solutions. Since there are extensive literatures \cite{koutsopoulos2013optimal,luo2014profit,zhang2014free,liu2014social} on the solutions to achieve strategyproofness in similar scenarios, we leave the discussions in Appendix \ref{sec:dsim}.

\subsection{An Example of Collusion on Strategyproof crowdsensing Game}
Unfortunately, a strategyproof incentive mechanism is usually not strong enough to resist collusion rigorously. 
{\color{black}
For example, suppose a game has two users $i,j$ s.t. $\kappa_i = \kappa_j = 1$. Given the user strategies $s_i$ and $s_j$, for user $i$ let its sensing time be $t_i(s_i, s_j)=s_j\mathrm{e}^{-s_i}$ and let its payment be $$p_i(s_i, s_j)=s_it_i(s_i, s_j)+\int_{s_i}^{+\infty}t_i(s, s_j)\mathrm{d}s=(s_i+1)s_j\mathrm{e}^{-s_i}.$$ The case of user $j$ is analogous. Thus the user utilities are 
\begin{equation}
\begin{aligned}
u_i(s_i,s_j)=&p_i(s_i, s_j)-\kappa_it_i(s_i, s_j) \\
=&(s_i+1)s_j\mathrm{e}^{-s_i} - 1\times s_j\mathrm{e}^{-s_i} \\
=&s_js_i\mathrm{e}^{-s_i},\\
\end{aligned}
\end{equation}
and similarly $u_j(s_i,s_j)=s_is_j\mathrm{e}^{-s_j}$. 
}
It can be shown this game is strategyproof. If both $i,j$ act truthfully, we have $u_i(1,1)=u_j(1,1)=1/e$, and each utility is maximized by fixing the other strategy to be 1. However, if both $i,j$ declare their cost units as 1.1, we have $u_i(1.1,1.1)=u_j(1.1,1.1)>0.4>1/e$ and thus $i,j$ can together conduct a valid collusion to achieve higher utilities. It is worth researching the criteria that any strategyproof game must satisfy in order to be collusion resistant. %In the following sections, we will show the quantitative relation between collusion and the parametric dependencies. The conception of parametric dependency is given by Definition \ref{def:pd}.
}
